---
title: "Analysis"
output: html_document
date: '2022-05-03'
---

```{r, echo = FALSE, message = FALSE}
source("../scripts/setup.R")
```




-------------------------------------------------------------------

NOUVEAU / ANALYSIS

-------------------------------------------------------------------




### For this first analysis, we are going to focus on the dataset Beef_US_price 

We want to know if we can forecast the US price of beef ust with the historical data. Going from jan 1984 to march 2022 (458 observations)

### Plotting the data US beef price (Converted to US Dollars per pounds = 453.6 grams)

```{r}
Beef_US_price.tsibble %>% autoplot(US_beef_price)+geom_line()
```

```{r}
p <- ggplot(Beef_US_price.tsibble, aes(x=DATE, y=US_beef_price)) +
  geom_line( color="steelblue") + 
  geom_point() +
  xlab("") +
  scale_y_continuous()

p
```

# Decompostion does not work 
```{r}
#Beef_US_price.tsibble %>% decompose(type="multiplicative") %>%
  #autoplot() + xlab("Year") +
  #ggtitle("Classical multiplicative decomposition")
# time series has no or less than 2 periods

```

```{r}
#beef_Comp <- decompose(Beef_US_price.tsibble)
```

With this non apparent pattern, we can try to apply the difference to the time serie. Making it non-sationnary could be helpful and apply an ARIMA model

----------------------------------------

### Apply the basics model (NAIVE, SNAIVE, MEAN)

## NAIVE model

```{r}
naive_mod <- naive(Beef_US_price.tsibble, h = 12)
summary(naive_mod)
```

```{r}
naive_mod %>% autoplot()
```


# SNAIVE model
```{r}
snaive_fit <- snaive(Beef_US_price.tsibble, h=12)
snaive_fit$mean
snaive_fit %>% autoplot()
```

# MEAN model


```{r}
mean_model <- Beef_US_price.tsibble%>% model(MEAN(US_beef_price))
forecast_mean_model <- mean_model %>% forecast(h = 12) 
forecast_mean_model
```

```{r}
mean_model %>% forecast(h = 12) %>% autoplot(Beef_US_price.tsibble)
```


```{r}
mean_model <- Beef_US_price.tsibble %>% model( Mean = MEAN(US_beef_price),
Naive = NAIVE(US_beef_price),
S_Naive = SNAIVE(US_beef_price))
forecast_mean_model <- mean_model %>% forecast(h = 12)
forecast_mean_model %>% autoplot(Beef_US_price.tsibble) +
guides(colour=guide_legend(title = "Forecast"))

```

# The accuracy 
```{r}
mean_model %>% accuracy
naive_mod %>% accuracy()
snaive_fit%>% accuracy()
```
The Naive model looks the best.


```{r}
checkresiduals(naive(Beef_US_price.tsibble))
```


----------------------------------------------


### ETS MODEL:


```{r}
fit.ANN <- Beef_US_price.tsibble %>%
  na.interp(Beef_US_price.tsibble)%>%
  model(ETS(US_beef_price ~ error("A") + trend("N") + season("N")))

fit.ANN %>% forecast(h = 12) %>% autoplot(Beef_US_price.tsibble) + theme(legend.position = "none")
fit.ANN %>% accuracy()
```

```{r}
fit..ANN <- Beef_US_price.tsibble %>%
model(ETS(US_beef_price ~ error("A") + trend("N") + season("N"), opt_crit = "mse"))
coefficients(fit..ANN)
```
According to the fit, we should set alpha = 1, which is exactly equal to the naive model, so the latest observation, these attempt in ETS, NAIVE or MEAN look unrelevant...

```{r}
FIT.ANN <- Beef_US_price.tsibble %>%
model(ETS(US_beef_price ~ error("A") + trend("N", alpha = 0.99) + season("N")))
FIT.ANN %>% forecast(h = 12) %>% autoplot(Beef_US_price.tsibble) + theme(legend.position = "none")
FIT.ANN%>%accuracy()
```

```{r}
FIT.ANN %>% forecast(h = 12) %>% autoplot(Beef_US_price.tsibble) +
geom_line(aes(y = .fitted, colour = "Fitted"), data = augment(FIT.ANN)) +
ylab("US_Beef_price") + xlab("DATE")
```


```{r}
fit.A.A.N <- Beef_US_price.tsibble %>%
model(ETS(US_beef_price ~ error("A") + trend("A") + season("N")))
fit.A.A.N %>% forecast(h = 12) %>% autoplot(Beef_US_price.tsibble) + theme(legend.position = "none")
fit.A.A.N%>%accuracy()
```
Accuracy of 6.26  fit.A.A.N

```{r}
report(fit.A.A.N)
```

```{r}
fitAAN.<- Beef_US_price.tsibble %>%
model(ETS(US_beef_price ~ error("A") + trend("A",alpha = 0.995, beta = 0.00477) + season("N")))
fitAAN. %>% forecast(h = 12) %>% autoplot(Beef_US_price.tsibble) + theme(legend.position = "none")
fitAAN.%>%accuracy()
```

```{r}
fitAAA<- Beef_US_price.tsibble%>% model(
additive = ETS(US_beef_price ~ error("A") + trend("A") + season("A")))
fc <- fitAAA %>% forecast(h = "1 years")
fc %>% autoplot(Beef_US_price.tsibble)
fitAAA%>%accuracy()
```


```{r}
fit.AAM <- Beef_US_price.tsibble %>% model(
additive = ETS(US_beef_price ~ error("A") + trend("A") + season("A")), multiplicative = ETS(US_beef_price ~ error("M") + trend("A") + season("M")))
fc <- fit.AAM %>% forecast(h = "1 years")
fc %>% autoplot(Beef_US_price.tsibble, size = c(1.2)) + xlab("DATE")
fit.AAM%>% accuracy()
```

# FINAL MODEL ETS with best accuracy

```{r}
fitAAA %>% forecast(h = 12) %>% autoplot(Beef_US_price.tsibble) +
geom_line(aes(y = .fitted, colour = "Fitted"), data = augment(fitAAA)) +
ylab("US_beef_price") + xlab("DATE")
```

Best accuracy result is for ETS(AAA)


### Time series Cross Validation

```{r}
beef.US_tr <- Beef_US_price.tsibble %>% slice(1:(n()-1)) %>% stretch_tsibble(.init = 3, .step = 1)
head(beef.US_tr)
```

```{r}
fc <- beef.US_tr %>% model(NAIVE(US_beef_price)) %>% forecast(h = 1)
fc
```

```{r}
fc %>% accuracy(Beef_US_price.tsibble)
```

```{r}
fitAAA %>% accuracy()
```

The ETS model (A,A,A) is not significantly improving the most basic forecast NAIVE model



- All of theses analysis demonstrate that it is extremely hard to get a good accurate forecast.

-----------------------------------------------------------------------------------------------------------------


--------------------------------------------
### Forecast a Time Series with ARIME
--------------------------------------------


#### Non-Stationnary forecast analysis 

# Differencing the data
```{r}
# Apply the first difference to the dataset beef_data.tsibble
Beef_US_price.tsibble %>% autoplot(log(US_beef_price))
Beef_US.diff <- Beef_US_price.tsibble %>% autoplot(log(US_beef_price) %>% difference())
Beef_US.diff
```
The data transformations of differencing make this time series stationary


### AUTO ARIMA model: With no missing value

```{r}
Beef_US_price2 <- Beef_US_price %>%
  na_interpolation()

beefTS1 = ts(Beef_US_price2)
arima_fit = auto.arima(beefTS1[,1])
plot(beefTS1[,2])
arima_fit1 = auto.arima(beefTS1[,2])
arima_forecast = forecast(arima_fit1, h = 12)
plot(arima_forecast)

```




```{r}
beefTS = ts(Beef_US_price)
arima_fit2 = auto.arima(Beef_US_price[,1])
plot(beefTS[,2])
arima_fit2 = auto.arima(beefTS[,2])
arima_forecast = forecast(arima_fit2, h = 12)
plot(arima_forecast)
```

```{r}
arima_fit1 %>% accuracy()
```
```{r}
arima_fit2 %>% accuracy()
```

```{r}
Beef_US_price.tsibble %>%
  gg_tsdisplay(difference(US_beef_price), plot_type='partial')
```







```{r}
fit.arima <- Beef_US_price.tsibble %>%
  model(ets = ETS(US_beef_price ~ trend("A"),arima = ARIMA(US_beef_price)))

fit.arima

```






-------------------------------------------------------------------------------------


--------------------------------------------
### Forecast a Time Series Regression Model
--------------------------------------------

Average Price: Ground Beef, 100% Beef (Cost per Pound/453.6 Grams) in U.S. City Average

------------------------------------------------


## Evolution of global price of beef with Time 
# Global_price_of_beef VS DATE

```{r}
mod0 <- lm(US_beef_price ~ DATE, data = Beef_US_price)
summary(mod0)
```
According to the regression mod0, each month, the  price of beef would increase of 2.31e-04 dollars .

---------------------------------------------------------------------------------------------------------------



## Graphical representation of  US_beef_price VS production and Consumption and Corn Price


```{r}
Annual_US_beef.price <- Beef_US_price
Annual_US_beef.price$DATE <- as.Date(Annual_US_beef.price$DATE )
Annual_US_beef.price$Year <- year(Annual_US_beef.price$DATE)
Annual_US_beef.price$Year <- format(Annual_US_beef.price$DATE,format="%Y")
Annual_US_beef.price <- aggregate(US_beef_price ~ Year, Annual_US_beef.price, mean)
Annual_US_beef.price[2] <- Annual_US_beef.price[2]*100

Annual_US_beef.price$Year <- as.Date(as.character(Annual_US_beef.price$Year), format = "%Y")

Annual_US_beef.price.ts <- Annual_US_beef.price %>%
  mutate(Year = year(Year)) %>%
  as_tsibble(index = Year)

Annual_US_beef.price.ts %>% autoplot()
names(Annual_US_beef.price.ts)[1] <- 'DATE'
```



### Merging in Total

Is there a link between the annual price and the annual production of beef ? Our assumption is: the more the production increases, it means the demand is higher. Therefore the more the price should increase
```{r}
Total <- merge(Annual_US_beef.price.ts, Beef_US_production.tsibble, by = 'DATE')
Total <- merge(US_Beef_consumption.ts, Total, by = 'DATE')
Total[4] <- Total[4]/100000
```

```{r}
v = c(Total$DATE)
Total$DATE <- as.Date(paste(v), format("%Y"))

Total.ts <- Total %>%
  as_tsibble(index = DATE)

```



```{r}
Total %>% GGally::ggpairs(columns = 2:4)
```


```{r}
fitTSLM <-  Total.ts %>% model(TSLM(US_beef_price ~ US_beef_production + US_beef_consumption )) %>%
report()
```

```{r}
fitTSLM2 <-  Total.ts %>% model(TSLM(US_beef_price ~ US_beef_production)) %>%
report()
```

```{r}
mod2 <- lm(US_beef_price ~ US_beef_production, data = Total.ts)
summary(mod2)
```

```{r}
cor(Total.ts$US_beef_production, Total.ts$US_beef_price)
```

```{r}
ggplot(Total.ts,
aes(x = US_beef_production,
y = US_beef_price)) + geom_point()+
    geom_smooth(method="lm", se=TRUE)
```


```{r}
checkresiduals(mod2)
```


### Merging in Tot - US Beef Price VS Corn Price
```{r}
Tot <- merge(Beef_US_price.tsibble, Corn_price_US.tsibble, by = 'DATE')
Tot <- merge(Tot, Nasdaq.tsibble, by = 'DATE')
Tot.ts <- as_tsibble(Tot, index = DATE)
```


```{r}
cor(Tot.ts$US_corn_price, Tot.ts$US_beef_price)
```

```{r}
cor(Tot.ts$Close, Tot.ts$US_beef_price)
```


# TSLM study: US_beef_price ~ Close + US_corn_price + DATE
```{r}
fitTSLM3 <-  Tot.ts %>% model(TSLM(US_beef_price ~ Close + US_corn_price + DATE)) %>%
report()
mod3 <- lm(US_beef_price~Close + US_corn_price, data = Tot)
```


```{r}
fitTSLM3 %>% gg_tsresiduals()
```

```{r}
fitTSLM4<-  Tot.ts %>% model(TSLM(US_beef_price ~ Close)) %>%
report()
```

```{r}
augment(fitTSLM4) %>%
ggplot(aes(x = DATE)) +
geom_line(aes(y = US_beef_price, colour = "US_beef_price")) +
geom_line(aes(y = .fitted, colour = "Close")) + xlab("Year") + ylab(NULL) + guides(colour = guide_legend(title='Nasdaq index VS US Beef price'))
```


```{r}
ggplot(Tot.ts,
aes(x = Close,
y = US_beef_price)) + geom_point()+
    geom_smooth(method="lm", se=TRUE)
```

```{r}
fitTSLM4 %>% gg_tsresiduals()
```



## Corn Price 

```{r}
fitTSLM5 <-  Tot.ts %>% model(TSLM(US_beef_price ~  US_corn_price)) %>%
report()
```

```{r}
ggplot(Tot.ts,
aes(x = US_corn_price,
y = US_beef_price)) + geom_point()+
    geom_smooth(method="lm", se=TRUE)
```



```{r}
fitTSLM5 %>% gg_tsresiduals()
```



## Plotting regression prediction:

```{r}
Tot.tsi <- ts(Tot, start=c(1990,1), end=c(2021, 11), frequency = 12)
```


```{r}
fit.price <- tslm(US_beef_price ~ US_corn_price + Close, data = Tot.tsi)
h <- 12

fcast.down <- forecast(fit.price,
  newdata = data.frame(US_corn_price = rep(200, h),
                       Close= rep(10000,h)))

fcast.up <- forecast(fit.price,
  newdata = data.frame(US_corn_price = rep(350, h),
                       Close= rep(12000,h)))

autoplot(Tot.tsi[, "US_beef_price"])+
  ylab("% change in US consumption") +
  autolayer(fcast.down, series = "down",
    PI = TRUE) +
  autolayer(fcast.up, series = "up",
    PI = TRUE) +
  guides(colour = guide_legend(title = "Scenario"))

```

```{r}
fit.price <- tslm(US_beef_price ~ US_corn_price, data = Tot.tsi)
h <- 12

fcast.down <- forecast(fit.price, newdata = data.frame(US_corn_price = rep(150, h)))

fcast.up <- forecast(fit.price, newdata = data.frame(US_corn_price = rep(350, h)))

autoplot(Tot.tsi[, "US_beef_price"])+
  ylab("US_beef_price") +
  autolayer(fcast.down, series = "down",
    PI = TRUE) +
  autolayer(fcast.up, series = "up",
    PI = TRUE) +
  guides(colour = guide_legend(title = "Scenario"))

```


##Covariance matrix

```{r}
cov(Tot[2:4])
```
The values along the diagonals of the matrix are simply the variances for each obsvervation:

The other values in the matrix represent the covariances between the various time series observations:

A positive number for covariance indicates that two variables tend to increase or decrease simultaneously.
For example, US_beef_price and Close have a positive covariance (246054), which indicates that observation that score high on Close also tend to score high on US_beef_price.

--------------------------------------------------------------

## Cross correlation:


```{r}
print(ccf(Corn_price_US.tsibble, Beef_US_price.tsibble))
```

This tells us that the correlation is higest at a lag of -1.833 month.


````{r}
print(ccf(Nasdaq.tsibble, Beef_US_price.tsibble))
```


--------------------------------------------------------------------------------------

----------------------------------------------------
### Forecast a Time Series with DYNAMIC REGRESSION
----------------------------------------------------

```{r}
autoplot(Tot.tsi[,2:4], facets = TRUE)
```

-------------------------------------------------

NOT RELEVANT 

-------------------------------------------------



```{r}
(fit.r <- auto.arima(Tot.tsi[,"US_beef_price"],
  xreg=Tot.tsi[,"US_corn_price"]))
```
Equation : 0.835 - 0.021x + nt

```{r}
cbind("Regression Errors" = residuals(fit.r, type="regression"),
      "ARIMA errors" = residuals(fit.r, type="innovation")) %>%
  autoplot(facets=TRUE)
```
The regression used for US_Beef price, based on the Corn price is not really efficient, as we can see it cannot explain the variation of the beef price. Arima explains it better with one differentinfg, but it remains some errors. in 2013 and in 2021. 


```{r}
checkresiduals(fit.r)
```

# With the Nasdaq index 
```{r}
(fit.r2 <- auto.arima(Tot.tsi[,"US_beef_price"],
  xreg=Tot.tsi[,"Close"]))
```



-------------------------------------------------

NOW RELEVANT 

-------------------------------------------------


BASED ON THE CORN PRICE ARIMA REGRESSION:

```{r}
fcast <- forecast(fit.r, xreg=rep(mean(Tot.tsi[,2]),12))
autoplot(fcast) + xlab("Year") +
  ylab("Percentage change")
```

```{r}
xreg <- cbind(US.corn = Tot.tsi[, "US_corn_price"],
              Nasdaq = Tot.tsi[, "Close"])
fit <- auto.arima(Tot.tsi[, "US_beef_price"], xreg = xreg)

checkresiduals(fit)
```




